Supplemental Information: Continuous developmental changes in word recognition support language learning across early childhood

### 2025-10-16 paper/supplemental_information.Rmd
minor changes to allow for rendering

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE)
library(here)
source(here("helper","common.R"))
#library(kableExtra)
library(papaja)

#set to TRUE to fit the Bayesian models
FIT_BAYES = FALSE
```

>>>>

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE)
library(here)
source(here("helper","common.R"))
#library(kableExtra)
library(papaja)
# library(fitdistrplus)
# library(statmod)
# library(gamlss.dist)
# library(semoutput)

#set to TRUE to fit the Bayesian models
FIT_BAYES = TRUE
```
